Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds

### 2021-01-18 Manuscript_Publication.Rmd
add tex

Sexual dimorphism due to competition within sexes contrasts with the drivers of sexual dichromatism. Plumage dichromatism can evolve as a consequence of female cryptic choice and be related to extra-bond fertilizations, but not necessarily paternal care or mating system [@owens_1998]. It can also arise as a result of selection on the level of crypsis of the sex that cares for offspring [@Dale_2015]. The fact that traits linked with competition (such as size dimorphism) are the ones associated with higher $\lambda_{DR}$ values – rather than sexual dichromatism – supports the general view that antagonistic interactions and sexual conflict can lead to increased diversity [@Bonduriansky_2011; @Tinghitella_2018; @Qvarnstrom_2012; @tsuji2020sexual]. Moreover, body size is a trait that influences multiple aspects of the physiology and ecology of a species. Differences in body size (as a result of sexual selection) could be linked to changes in diet, vulnerability to predators or environmental tolerance [@Damuth_1993; @Liow_2008; @Bonduriansky_2011], and such differences could ultimately increase the likelihood of divergence between young lineages. In mammals, sexual selection is suggested to have driven the evolution of large body size which in turn has allowed diversification of ecological strategies in the clade, and higher speciation rates [@Mclain_1993; @Bonduriansky_2011].

@@

\phantomsection
# Data Accessibility
We have sought to make the data and Supplementary Material (including `R` code) freely accessible to readers. The code and Supplementary Material for this manuscript are available on \href{https://justincally.github.io/SexualSelection_Speciation/}{GitHub} and as an attached HTML document (Supplementary Material) for reviewers. Data is archived in the adjoined GitHub repository and will be made publicly available on acceptance.

>>>>

Sexual dimorphism due to competition within sexes contrasts with the drivers of sexual dichromatism. Plumage dichromatism can evolve as a consequence of female cryptic choice and be related to extra-pair fertilizations, but not necessarily paternal care or mating system [@owens_1998]. It can also arise as a result of selection on the level of crypsis of the sex that cares for offspring [@Dale_2015]. The fact that traits linked with competition (such as size dimorphism) are the ones associated with higher $\lambda_{DR}$ values – rather than sexual dichromatism – supports the general view that antagonistic interactions and sexual conflict can lead to increased diversity [@Bonduriansky_2011; @Tinghitella_2018; @Qvarnstrom_2012; @tsuji2020sexual]. Moreover, body size is a trait that influences multiple aspects of the physiology and ecology of a species. Differences in body size (as a result of sexual selection) could be linked to changes in diet, vulnerability to predators or environmental tolerance [@Damuth_1993; @Liow_2008; @Bonduriansky_2011], and such differences could ultimately increase the likelihood of divergence between young lineages. In mammals, sexual selection is suggested to have driven the evolution of large body size which in turn has allowed diversification of ecological strategies in the clade, and higher speciation rates [@Mclain_1993; @Bonduriansky_2011].

@@

\phantomsection
# Data Accessibility
We have sought to make the data and Supplementary Material (including `R` code) freely accessible to readers. The code and Supplementary Material for this manuscript are available on \href{https://justincally.github.io/SexualSelection_Speciation/}{GitHub} and as an attached HTML document (Supplementary Material) for reviewers. Data is archived in the adjoined GitHub repository and the environmental dataset collated for this manuscript is available on Dryad: https://doi.org/10.5061/dryad.573n5tb6n.
